Edge sign prediction in general graphs and connection with Correlation Clustering

### 2017-06-28 notations.tex
clarify and expand notations

\begin{table*}[htpb]
  \centering
  \caption{List of notations used in this thesis}\label{tab:notations}%
  \vspace{-.5\baselineskip}
  \begin{tabulary}{187mm}{LL}
    \toprule
    Symbol & Meaning \\
    \midrule
    $G$ & A graph, either directed or undirected \\
    $V$, $V_t$ & The set of all the nodes of a graph. Unless noted otherwise, nodes are indexed from $1$ to $|V|$ \\
    $E$, $E_t$ & The set of all the edges of a graph \\
    $\degr(u)$ & The total degree of node $u$ (that is the number of edges incident to $u$
    regardless of their direction) \\
    $(u,v)$, $(i,j)$ & An undirected edges between nodes $u$ and $v$ (or $i$ and $j$) \\
    $\mathcal{N}(u)$ & The set of all neighbors of $u$, regardless of edge direction. We thus have
    $|\mathcal{N}(u)| = \degr(u)$ \\
    \bottomrule
  \end{tabulary}
\end{table*}

>>>>

\begin{table*}[thpb]
  \centering
  \caption{List of notations used in this thesis}\label{tab:notations}%
  \vspace{-.5\baselineskip}
  \begin{tabulary}{187mm}{LL}
    \toprule
    Symbol & Meaning \\
    \midrule
    $G$ & An unweighted graph, that can be either directed or undirected \\
    $V$ & The set of all the nodes of a graph, with $|V|=n$. Unless noted otherwise, nodes are indexed from $1$ to $n$ \\
    $E$ & The set of all the edges of a graph, with $|E|=m$ \\
    $u$ & A generic node of $G$. When referring to several nodes, we naturally use $u$, $v$, $w$ and so on. \\
    $(u,v)$ & An undirected edge between nodes $u$ and $v$ \\
    % \euv{} & A directed edge from node $u$ to node $v$ \\
    $\yuv{}$ & The sign of the edge $(u,v)$, which can be either $+1$ or $-1$ \\
    $Y(E)$ & The labeling of $E$, that is the set of all signs of $E$: $Y(E) = \{\yuv , (u,v)\in E\}$ \\
    $\etrain$ & A subset of $E$, given or chosen, of which we observe the signs \\
    $\degr(u)$ & The total degree of node $u$ (that is, the number of edges incident to $u$,
    regardless of their direction) \\
    $\mathcal{N}(u)$ & The set of all neighbors of $u$, regardless of edge direction. It thus holds
    that $|\mathcal{N}(u)| = \degr(u)$ \\
    $T$ & An unweighted and undirected tree \\
    $\pathtuv$ & The unique path between $u$ and $v$ in the tree $T$, represented by an ordered list of edges \\
    $|\pathtuv|$ & The length of the path between $u$ and $v$ in the tree $T$, that is its number of edges \\
    \bottomrule
  \end{tabulary}
\end{table*}
